An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-06-28 EconGrowth.Rnw
Changed to -- from - in LaTeX code.

The following tables show covariances among GDP ($y$) and 
factors of production ($k$, $l$, $q$, $x$, and $u$). 
Covariances are calculated for the following years: 
\begin{itemize}
  \item{1980-2011 for covariances among 
        $y$, $k$, $l$, $q$, and $x$ for developed\\*economies;}
  \item{1980-2000 for covariances involving 
        $u$ for developed economies; and}
  \item{1991-2011 for covariances among 
        $y$, $k$, $l$, $q$, and $x$ for developing\\*economies.}
\end{itemize}

>>>>

The following tables show covariances among GDP ($y$) and 
factors of production ($k$, $l$, $q$, $x$, and $u$). 
Covariances are calculated for the following years: 
\begin{itemize}
  \item{1980--2011 for covariances among 
        $y$, $k$, $l$, $q$, and $x$ for developed\\*economies;}
  \item{1980--2000 for covariances involving 
        $u$ for developed economies; and}
  \item{1991--2011 for covariances among 
        $y$, $k$, $l$, $q$, and $x$ for developing\\*economies.}
\end{itemize}
